A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2012-02-06 papers/contact/paper.tex
add nicer plots for contact monte-carlo data Tested everything on collins.
minor edit on contact paper Tested everything on bingley.

%\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...

@@

@@

A final definition of the inhomogeneous contact density would be the
contact density for spheres \emph{touching at a given point}.  This
would be a symmetric measure, since both spheres involved are treated
in the same way.  In fact, the density of such spheres is just the
density $n_0(\xx)$ from FMT.  See Figure~\ref{fig:n0} for an
illustration $n_0$.  Since $n_0$ is the fundamental measure of sphere
surface contact, it would make sense to define a contact density that
would correspond.

To find the contact density at a given point of contact, we can't
simply change the radius for spheres touching that point, since that
would give us the pressure averaged over the entire surface of those
spheres.  Instead, we would have to imagine extending a patch of those
spheres which is located at the point of interest, as illustrated in
Figure~\ref{fig:contact}.  \textcolor{red}{I'm not sure how to go
  about doing this.  In the derivation section, I have some ideas
  jotted down, but they don't really work.}

@@

\begin{figure}
\includegraphics[width=5cm]{figs/contact}
\caption{Construction for finding the contact density at a given point
  of contact.  We envision a small area $dA$ of each sphere that touches
the point $\mathbf{r}$ extended by a distance $dR$.}
\label{fig:contact}
\end{figure}

@@

>>>>

\newcommand{\derivation}[1]{#1} % Use this to show all derivations in detail
%\newcommand{\derivation}[1]{} % Use this for nice pegagogical paper...

@@

%\input{formulas}

@@

An alternate definition of the inhomogeneous contact density would be
the contact density for spheres \emph{touching at a given point}.
This would be a symmetric measure, since both spheres involved are
treated in the same way.  In fact, the density of such spheres is just
the density $n_0(\xx)$ from FMT.  See Figure~\ref{fig:n0} for an
illustration $n_0$.  Since $n_0$ is the fundamental measure of sphere
surface contact, it would make sense to define a contact density that
would correspond.  This is what is done by Yu and
Wu\cite{yu2002fmt-dft-inhomogeneous-associating}, as discussed in
Section~\ref{sec:yuwu}.

@@

@@

%% \begin{widetext}
%% \section{Formulas generated from Haskell}

%% \begin{align}
%%   \Phi_1 &= \phione \\
%%   \Phi_2 &= \phitwo \\
%%   \Phi_3 &= \phithree \\
%%   \frac{d F}{dn_3} &= \dwbdnthree \\
%%   \frac{d F}{dn_2} &= \dwbdntwo \\
%%   \frac{d F}{dn_1} &= \dwbdnone \\
%%   \frac{d F}{d\vec{n}_{2v}} &= \dwbdntwov \\
%%   \frac{d F}{d\vec{n}_{1v}} &= \dwbdnonev \\
%% \end{align}
%% \end{widetext}
